Easy as Pi: A Network Coding Raspberry Pi Testbed

### 2016-06-04 measurements.tex
Preparing for energy and power section

\begin{figure}[ht!]
\centering
\includegraphics[width=0.5\textwidth]{images/2015-04-18_encoding_decoding_1024.eps}
\caption{Encoding and Decoding performance for g = 1024 \cite{wunderlich2015network}}
\label{enc_dec1024}
\end{figure}

@@

\begin{figure}[ht!]
\centering
\includegraphics[width=0.5\textwidth]{images/2015-04-18_encoding_decoding_128.eps}
\caption{Encoding and Decoding performance for g = 128 \cite{wunderlich2015network}}
\label{enc_dec128}
\end{figure}

@@

\begin{figure}[ht!]
\centering
\includegraphics[width=0.5\textwidth]{images/2015-04-18_encoding_decoding_16.eps}
\caption{Encoding and Decoding performance for g = 16 \cite{wunderlich2015network}}
\label{enc_dec16}
\end{figure}

@@

% \begin{figure}
% \centering
% \begin{subfigure}[b]{0.3\textwidth}
% \includegraphics[width=\textwidth]{images/2015-04-18_encoding_decoding_1024.eps}
% \caption{Encoding and Decoding performance for g = 1024}
% \label{enc_dec1024}
% \end{subfigure}
%
% \begin{subfigure}[b]{0.3\textwidth}
% \includegraphics[width=\textwidth]{images/2015-04-18_encoding_decoding_128.eps}
% \caption{Encoding and Decoding performance for g = 128}
% \label{enc_dec128}
% \end{subfigure}
%
% \begin{subfigure}[b]{0.3\textwidth}
% \includegraphics[width=\textwidth]{images/2015-04-18_encoding_decoding_16.eps}
% \caption{Encoding and Decoding performance for g = 16}
% \label{enc_dec16}
% \end{subfigure}
% \end{figure}

@@

To compare how much slower is the matrix multiplication with respect to the
matrix inversion for different generation sizes, we ran a set of tests. We used
a single core to perform the operations. We changed the generation sizes,
performed matrices multiplications and matrix inversions, and measured the time
spent doing so. We then calculated the ratio between these two measured times
times $ratio = \frac{T_{mult}}{T_{inv}}$. Table~\ref{runtimes} summarizes the
results. The bigger the matrix size, the smaller is the calculated ratio. This
means that when the problems are bigger, the decoding throughput decreases
compared with the encoding throughput.

\begin{table}[H]
\center
\caption{Multiplication and inversion run-times for different generation sizes with 1 thread}
\begin{tabular}{|r|r|r|r|}
\hline
g & multiplication (ms) & inversion (ms) & ratio \\
\hline
\hline

>>>>

\begin{figure}[ht!]
\centering
\includegraphics[width=0.5\textwidth]{images/2015-04-18_encoding_decoding_1024.pdf}
\caption{Encoding and Decoding performance for g = 1024 \cite{wunderlich2015network}}
\label{enc_dec1024}
\end{figure}

@@

\begin{figure}[ht!]
\centering
\includegraphics[width=0.5\textwidth]{images/2015-04-18_encoding_decoding_128.pdf}
\caption{Encoding and Decoding performance for g = 128 \cite{wunderlich2015network}}
\label{enc_dec128}
\end{figure}

@@

\begin{figure}[ht!]
\centering
\includegraphics[width=0.5\textwidth]{images/2015-04-18_encoding_decoding_16.pdf}
\caption{Encoding and Decoding performance for g = 16 \cite{wunderlich2015network}}
\label{enc_dec16}
\end{figure}

@@

@@

To compare how much slower is the matrix multiplication with respect to the
matrix inversion for different generation sizes, we ran a set of tests. We used
a single core to perform the operations. We changed the generation sizes,
performed matrices multiplications and matrix inversions, and measured the time
spent doing so which we name $T_{mult}$ and $T_{inv}$. We calculate the ratio
between these two measured times defined as $r = \frac{T_{mult}}{T_{inv}}$.
Table~\ref{runtimes} summarizes the results. The bigger the matrix size, the
smaller is the calculated ratio. This means that when the problems are bigger,
the decoding throughput decreases compared with the encoding throughput.

\begin{table}[H]
\center
\caption{Multiplication and inversion run-times for different generation sizes with 1 thread}
\begin{tabular}{|r|r|r|r|}

\hline
$g$ & $T_{mult}$ (ms) & $T_{inv}$ (ms) &$r$ \\
\hline
\hline

### 2016-06-04 metrics.tex
Preparing for energy and power section

\subsection{Energy Consumption}
In large-scale networks where several Raspberry Pis might be deployed,
both overall and per-bit energy consumption of the devices during the
encoding and decoding process are relevant parameters that impact in the
network performance for a given coding scheme. To compute the

\subsubsection{Average}
\subsubsection{Per-Bit}

>>>>

\subsection{Power and Energy Consumption}
In large-scale networks where several Raspberry Pis might be deployed,
both overall and per-bit energy consumption of the devices during the
encoding and decoding process are relevant parameters that impact in the
network performance for a given coding scheme. To compute the

\subsubsection{Average Power}
\subsubsection{Energy Consumption}
